Top Tens

### 2017-03-10 San Antonio/top_tens.Rmd
simple linear model
y = num.days.lost or num.death

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

@@

```{r top 10 based on num.days.lost}
complete.active.quarters %>% filter(mine_id == 101322) %>% select(mine.name, year, quarter, last.year.lost) %>% head(10)
```

>>>>

@@

```{r top 10 based on certain mine}
complete.active.quarters %>% filter(mine_id == 101322) %>% select(mine.name, year, quarter, last.year.lost) %>% head(10)
```

```{r simple lm}
load("./San Antonio/output/result.RData")
summary(lm(1*num.death+0*num.days.lost+0*num.days.restrict~last.quarter.lost+last.year.lost+last.three.years.lost
           +last.quarter.restrict+last.year.restrict+last.three.years.restrict
           +last.quarter.viol+last.year.viol+last.three.years.viol
           +last.quarter.death+last.year.death+last.three.years.death, 
           data=complete.active.quarters %>% filter(active)))

summary(lm(num.death~last.three.years.lost+last.quarter.viol+last.year.viol, data=complete.active.quarters %>% filter(active)))
```
